\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex

Next, we define a vector of three parameters:
\begin{align}
\hat{\Vec{y}} &= \bbm \alpha & \beta & \gamma \ebm^T = \frac{1}{\hat{Z}^{(j)}_{C_1}} \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & 1 \ebm ^T
\end{align}
The feature position in camera frame $C_i$ can be expressed as
\begin{align}
\hat{\Vec{p}}_{C_i}^{f_j C_i} = \hat{\Vec{C}}_{i1} \hat{\Vec{p}}_{C_1}^{f_j C_1}  + \hat{\Vec{p}}_{C_i}^{C_1 C_i}
\end{align}
With our state parameters, we can use this equation to define three functions:
\begin{align}
    \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \\ h_3 (\hat{\Vec{y}}) \ebm 
    & = \hat{\Vec{C}}_{i1} \bbm \alpha \\ \beta \\ 1 \ebm + \gamma  \hat{\Vec{p}}_{C_i}^{C_1 C_i} \notag \\
    & = \bbm C_{11} \alpha + C_{12} \beta + C_{13} + \gamma \hat{x}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{21} \alpha + C_{22} \beta + C_{23} + \gamma \hat{y}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{31} \alpha + C_{32} \beta + C_{33} + \gamma \hat{z}_{C_i}^{C_1 C_i} 
        \ebm 
\end{align}
The camera measurement error can then be written as
\begin{align}
\Vec e(\hat{\Vec{y}}) = \hat{\Vec{z}}_i^{(j)} - \frac{1}{h_3 (\hat{\Vec{y}}) } \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \ebm
\end{align}
The least squares linear system then becomes
\begin{align}
(\Vec  E^T \Vec W ^{-1} \Vec E ) \delta \Vec{y}^*  = - \Vec{E}^T\Vec{W}^{-1}\Vec{e}(\hat{\Vec{y}})
\end{align}
where
\begin{align}
\Vec E &= \frac{\partial \Vec e}{\partial \hat{\Vec{y}}}
& &
\text{and}
&
\Vec W &= \text{diag}\left\{ \Vec{R}_1'^{(j)}, \hdots, \Vec{R}_N'^{(j)} \right\}
\end{align}
with $\Vec{R}_i'^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.

@@

If we linearize (\ref{eq:residual_def}) about the estimates for the camera pose and feature position, we obtain an estimate of the exteroceptive measurement error
\begin{align}
    \Vec{r}_i^{(j)} &\simeq \Vec{H}_{\Vec{x}, i}^{(j)} \widetilde{\Vec{x}}_i + \Vec{H}_{f, i}^{(j)} \widetilde{\Vec{p}}_G^{f_j G} + \Vec{n}_i^{(j)}
\end{align}
where $\Vec{H}_{\Vec{x}, i}^{(j)}$ and $\Vec{H}_{f, i}^{(j)}$ are the Jacobians of the measurement of feature $f_j$ from camera pose $i$ with respect to the filter state and the position of the feature, respectively.
These are given by
\begin{align}
    \Vec{H}_{\Vec{x}, i}^{(j)} &= \bbm \Vec{0} & \Vec{J}^{\left(j\right)}_i \left(\hat{\Vec{p}}_{C_i}^{f_j C_i}\right)^\times & -\Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G} & \Vec{0} \ebm \\
    \Vec{H}_{f, i}^{(j)} &= \Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G}
\end{align}
where the left $\Vec{0}$ in $\Vec{H}_{\Vec{x}, i}^{(j)}$ has dimension $2\times\left(12+6\left(i-1\right)\right)$, the right $\Vec{0}$ has dimension $2\times6\left(N-i\right)$, and
\begin{align}
    \Vec{J}^{\left(j\right)}_i &= \frac{1}{\left(\hat{Z}^{(j)}_{C_i}\right)^2}
    \bbm \hat{Z}^{(j)}_{C_i} & 0 & -\hat{X}^{(j)}_{C_i} \vspace{0.5em} \\
             0 & \hat{Z}^{(j)}_{C_i} & -\hat{Y}^{(j)}_{C_i}
    \ebm .
\end{align}
$\Vec{n}_i^{(j)}$ is a zero-mean Gaussian noise term with covariance matrix $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_u, \sigma^2_v\right\}$.

>>>>

Next, we define a vector of three parameters:
\begin{align}
\hat{\Vec{y}} &= \bbm \alpha & \beta & \gamma \ebm^T = \frac{1}{\hat{Z}^{(j)}_{C_1}} \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & 1 \ebm ^T
\end{align}
The feature position in camera frame $C_i$ can be expressed as
\begin{align}
\hat{\Vec{p}}_{C_i}^{f_j C_i} = \hat{\Vec{C}}_{i1} \hat{\Vec{p}}_{C_1}^{f_j C_1}  + \hat{\Vec{p}}_{C_i}^{C_1 C_i}
\end{align}
With our state parameters, we can use this equation to define three functions:
\begin{align}
    \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \\ h_3 (\hat{\Vec{y}}) \ebm 
    & = \hat{\Vec{C}}_{i1} \bbm \alpha \\ \beta \\ 1 \ebm + \gamma  \hat{\Vec{p}}_{C_i}^{C_1 C_i} \notag \\
    & = \bbm C_{11} \alpha + C_{12} \beta + C_{13} + \gamma \hat{x}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{21} \alpha + C_{22} \beta + C_{23} + \gamma \hat{y}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{31} \alpha + C_{32} \beta + C_{33} + \gamma \hat{z}_{C_i}^{C_1 C_i} 
        \ebm 
\end{align}
The camera measurement error can then be written as
\begin{align}
\Vec e(\hat{\Vec{y}}) = \hat{\Vec{z}}_i^{(j)} - \frac{1}{h_3 (\hat{\Vec{y}}) } \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \ebm
\end{align}
The least squares linear system then becomes
\begin{align}
(\Vec  E^T \Vec W ^{-1} \Vec E ) \delta \Vec{y}^*  = - \Vec{E}^T\Vec{W}^{-1}\Vec{e}(\hat{\Vec{y}})
\end{align}
where
\begin{align}
\Vec E &= \frac{\partial \Vec e}{\partial \hat{\Vec{y}}}
& &
\text{and}
&
\Vec W &= \text{diag}\left\{ \Vec{R}_1^{(j)}, \hdots, \Vec{R}_N^{(j)} \right\}
\end{align}
with $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.

@@

If we linearize (\ref{eq:residual_def}) about the estimates for the camera pose and feature position, we obtain an estimate of the exteroceptive measurement error
\begin{align}
    \Vec{r}_i^{(j)} &\simeq \Vec{H}_{\Vec{x}, i}^{(j)} \widetilde{\Vec{x}}_i + \Vec{H}_{f, i}^{(j)} \widetilde{\Vec{p}}_G^{f_j G} + \Vec{n}_i^{(j)}
\end{align}
where $\Vec{H}_{\Vec{x}, i}^{(j)}$ and $\Vec{H}_{f, i}^{(j)}$ are the Jacobians of the measurement of feature $f_j$ from camera pose $i$ with respect to the filter state and the position of the feature, respectively.
These are given by
\begin{align}
    \Vec{H}_{\Vec{x}, i}^{(j)} &= \bbm \Vec{0} & \Vec{J}^{\left(j\right)}_i \left(\hat{\Vec{p}}_{C_i}^{f_j C_i}\right)^\times & -\Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G} & \Vec{0} \ebm \\
    \Vec{H}_{f, i}^{(j)} &= \Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G}
\end{align}
where the left $\Vec{0}$ in $\Vec{H}_{\Vec{x}, i}^{(j)}$ has dimension $2\times\left(12+6\left(i-1\right)\right)$, the right $\Vec{0}$ has dimension $2\times6\left(N-i\right)$, and
\begin{align}
    \Vec{J}^{\left(j\right)}_i &= \frac{1}{\left(\hat{Z}^{(j)}_{C_i}\right)^2}
    \bbm \hat{Z}^{(j)}_{C_i} & 0 & -\hat{X}^{(j)}_{C_i} \vspace{0.5em} \\
             0 & \hat{Z}^{(j)}_{C_i} & -\hat{Y}^{(j)}_{C_i}
    \ebm .
\end{align}
$\Vec{n}_i^{(j)}$ is a zero-mean Gaussian noise term with covariance matrix $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.
